Fluent statistical computing interfaces for biological data analysis

### 2020-04-16 Rmd/01-intro.Rmd
update references

Chapter \@ref(ch:liminal) introduces
a software package called *liminal* for constructing these views and
a user interaction framework for identifying distortions. We present several
case studies for using our approach to diagnose the quality of 
results obtained via t-distributed stochastic neighbour embeddings (t-SNE)

>>>>

Chapter \@ref(ch:tsne) introduces
a software package called *liminal* for constructing these views and
a user interaction framework for identifying distortions. We present several
case studies for using our approach to diagnose the quality of 
results obtained via t-distributed stochastic neighbour embeddings (t-SNE)
